Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-14 paper/paper.tex
pass

\Fix{The
  closest work to ours was done by Patra and Pradel~\cite{patra2016learning},
  where they evaluated their proposed language-agnostic fuzzer to find
  cross-browser HTML+JS discrepancies. This project aims at building
  and evaluating an infrastructure for differential testing of runtime
  engines, such as the JS engine or WebAssembly's. The sensible parts
  of the infrastructure are the checks of input validity (as to reduce
  waste/cost) and output correctness (as to reduce false positives).}

RFC-Directed Differential Testing of Certificate Validation in SSL/TLS Implementations...[ICSE18]

>>>>

\subsection{Testing \js{} Engines}
\label{sec:testing-js-engines}
The closest work to ours was done by Patra and
Pradel~\cite{patra2016learning}, where they proposed a
language-agnostic fuzzer to find cross-browser HTML+JS
discrepancies. Their work aims at building and evaluating an
infrastructure for differential testing of runtime engines, such as JS
engines nd WebAssembly engines. The sensible parts of the
infrastructure are the checks of input validity (as to reduce
waste/cost) and output correctness (as to reduce false
positives). Patra and Pradel work differs from ours in that their main
contribution is analytical whereas our main contribution is
empirical--we aim at assessing reliability of \js\ engines and find
bugs on them using simple approaches, such as test transplantation.

Several fuzzing techniques have been proposed recently\Fix{...elaborate...}

\subsection{Differential Testing}
Several different applications of differential testing have been
proposed in recent years. Chen and
colleagues~\cite{Chen:2018:RDT:3180155.3180226} recently proposed a
technique to generate X.509 certificates based on Request For
Proposals (RFC) as specification with the goal of detecting bugs in
different SSL/TLS implementations. Those bugs can comprimise security
of servers which rely on these certificates to properly authenticate
the parties involved in a communication session. Lidbury and
colleagues~\cite{Lidbury:2015:MCF:2737924.2737986} and Donaldson and
colleagues~\cite{Donaldson:2017:ATG:3152284.3133917} have been
focusing on finding bugs in programs for graphic cards (\eg{},
OpenCL). These programs use the Single-Instruction Multiple-Data
(SIMD) programming abstraction and typically run on GPUs.  Perhaps the
application of differential testing that received most attention to
date was compiler testing. In 1972, Purdom~\cite{Purdom1972} proposed
the use of a generator of sentences from grammars to test correctness
of automatically generated parsers. After that, significant progress
has been made. Yang and
colleagues~\cite{Yang:2011:FUB:1993498.1993532} have proposed CSmith
to randomly create C programs from a grammar, for a subset of C, and
then check the output of these programs in different compilers (\eg{},
GCC and LLVM). Le and colleagues~\cite{Le:2014:CVV:2594291.2594334}
proposed the idea of ``equivalence modulo inputs'', which creates
variants of program which should have equivalent behavior compared to
the original, but for which the compiler manifests
discrepancy. Differential testing has also been applied to test
refactoring engines~\cite{Daniel:2007:ATR:1287624.1287651}, to test
symbolic engine implementations~\cite{Kapus:2017:ATS:3155562.3155636},
and to test disassemblers and binary
lifters~\cite{Paleari:2010:NDD:1831708.1831741,Kim:2017:TIR:3155562.3155609}. All
in all, it has shown to be flexible and effective for a wide range of
applications. Surprisingly, not much work has been done on
differential testing of \js\ engines. Mozilla uses differential
testing to look for discrepanices across different configurations of
the same version of its \smonkey\ engine (using the ``compare\_jit''
flag of jsfunfuzz~\cite{jsfunfuzz}) whereas we focus on discrepancy
across engines. Patra and Pradel evaluated their fuzzing strategy on
different browsers~\cite{patra2016learning} (see
Section~\ref{sec:testing-js-engines}).

\subsection{Testing \js\ Programs}
Patra and colleagues~\cite{Patra:2018:CFU:3180155.3180184} proposed a
lightweight approach to detect conflicts in \js\ libraries that occur
when names introduced by different libraries collide. This problem was
found to be common as the design of \js\ allows for overlaps in
namespaces. A similar problem has been investigated by Nguyen and
colleagues~\cite{nguyen-etal-icse2014} and Eshkevari and
colleagues~\cite{eshkevari-etal-icpc2014} in the context of PHP
programs, which are popular in the context of Content Management
Systems as WordPress. The focus of this paper is on testing
\js\ engines as opposed to \js\ programs. Our goal is therefore
orthogonal to theirs.

\section{Conclusions}

\Fix{...}
